\TheTitle

### 2015-08-17 linvis.tex
Conclusion: Finishing up conclusion
Okay, I think we are done adding content.
On to editing...

\section{Conclusion}

\evantodo{DO IT! JUST DO IT!}

@@

% \balance
\end{document}

>>>>

\section{Conclusion}
Our tool shows promising results, providing a clearer picture of the relation
between the merges and commits for sections of the kernel in relation to the
DAG-based models.  Not only are we able to provide a clearer visualization, we
are able to provide information about the files edited by all of the commits
contained within a merge.

While we are able to gather a better explanation of the changes happening at
each commit and merge, the tree-model requires more information than what is
provided by git, requiring a central server to monitor changes to the project.
This breaks the design goals of decentralized version control systems and makes
the tool specific to the project.

@@

\balance

\end{document}
